---
title: "Coursera Regression Models Project"
author: "Josh Starkey"
date: "February 28, 2016"
output: pdf_document
---
###Overview
This is a Coursera project for the Data Science Specialization: Regression Models Course.  The project is described https://www.coursera.org/learn/regression-models/peer/nxntd/regression-models-course-project.  This report is uploaded as a pdf, but the R Markdown is located https://github.com/star9475/RegrModelsProject/blob/master/RegrModelsProject.Rmd.

###Executive Summary
This project looks at a data set of a collection of cars. Explore the relationship between a set of variables and miles per gallon (MPG) (outcome), and answer the following two questions:

* Is an automatic or manual transmission better for MPG
* Quantify the MPG difference between automatic and manual transmissions

The analysis of the data shows there isn't an effect on mpg from the type of transmission.  The weight of the car has the biggest effect.

**The Dataset**

First, load libraries and the <code>mtcars</code> dataset:
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(usdm)
data(mtcars)
```
Typing <code>?mtcars</code> brings up the help for the mtcars dataset.  The format is as follows:

A data frame with 32 observations on 11 variables.

Column | var name | unit
-------|----------|-----
[, 1] | mpg | Miles/(US) gallon
[, 2] | cyl |	 Number of cylinders
[, 3] | disp |	Displacement (cu.in.)
[, 4] | hp | Gross horsepower
[, 5] | drat | Rear axle ratio
[, 6] | wt | Weight (lb/1000)
[, 7] | qsec | 1/4 mile time
[, 8] | vs | V/S
[, 9] | am | Transmission (0 = automatic, 1 = manual)
[,10] | gear | Number of forward gears
[,11] | carb | Number of carburetors

**Exploratory Analysis**
```{r}
summary(mtcars)
str(mtcars)
head(mtcars)
```

**Explore with Graphs**

```{r, fig.align="left", warning=FALSE,message=FALSE, echo=FALSE}

ggplot(mtcars, aes(x=factor(am), y=mpg, color=factor(am))) +
     geom_boxplot() +
     scale_color_manual(values=c("blue", "red")) +
     geom_point(size=2, position="jitter") +
     labs(title ="Mtcars Box Plot", y="MPG", x="Transmission type") +
     coord_cartesian() +
     theme_minimal()
#plot_ly(mtcars, y = mpg, color = factor(am), type = "box")
```

**Fit a model**

```{r, cache=TRUE}
summary(lm(mpg ~ . , data = mtcars))
```
The coefficients <code>wt</code> and <code>am</code> have the most significance and correlation to the outcome variable <code>mpg</code>.  

Refit the model with just these factors
```{r, cache=TRUE}
model1 <- lm(mpg ~ factor(am) -1, mtcars)
model2 <- lm(mpg ~ wt, mtcars)
model3 <- lm(mpg ~ factor(am) -1 + wt, mtcars)

summary(model1)
summary(model2)
summary(model3)
```
The model 2 and 3 have similar R-squared values.  Since the desire was to show the transmission type with respect to mpg, let's use model 3 with both transmission and weight.

**Describe the Coefficients**
```{r}
model1$coefficients
model3$coefficients
```
There's a reduction in about 5 mpg for every 1000 lbs of weight.  By itself, it looks like the transmission type has a 10 mpg affect on the car.  However <code>model3</code>shows weight has a bigger effect. 

**Residual Plots of Selected Model**
```{r, warning=FALSE,message=FALSE}
par(mfrow = c(2, 2))
plot(model3)
```
The residual plots show nothing significant.

**Confidence Intervals**
```{r}
confint(model3, 'wt')
```
In the data set, the 95% confidence interval of the weight is -6.964 to -3.741 thousands per mpg.


