---
title: "Coursera Regression Models Project"
author: "Josh Starkey"
date: "February 3, 2016"
output: html_document
---

##Executive Summary

First, let's load libraries and the <code>mtcars</code> dataset:
```{r, warning=FALSE, message=FALSE, cache=TRUE}
library(ggplot2)
data(mtcars)
```

###Exploratory Analysis
```{r}
str(mtcars)
```

Explore with Graphs

```{r, fig.align="left", cache = TRUE, warning=FALSE,message=FALSE, echo=FALSE}
p <- ggplot(mtcars, aes(x=factor(am), y=mpg, color=factor(am))) +
     geom_violin(scale = "width", trim=TRUE) +
     scale_color_manual(values=c("blue", "red")) +
     geom_point(size=2, position="jitter") +
     labs(title ="Mtcars Violin Plot", y="MPG", x="Transmission type") +
     theme_minimal()
p
```
###Criteria
Fit the linear model
```{r}
fit <- lm(mpg ~ factor(am), mtcars)

summary(fit)
```

Did the student interpret the coefficients correctly?
Did the student do some exploratory data analyses?
Did the student fit multiple models and detail their strategy for model selection?
Did the student answer the questions of interest or detail why the question(s) is (are) not answerable?
Did the student do a residual plot and some diagnostics?
Did the student quantify the uncertainty in their conclusions and/or perform an inference correctly?
Was the report brief (about 2 pages long) for the main body of the report and no longer than 5 with supporting appendix of figures?
Did the report include an executive summary?
Was the report done in Rmd (knitr)?
